Supplemental Materials: Polymethylation Scores for Prenatal Maternal Smoke Exposure Persist Until Age 15 and Are Detected in Saliva

### 2021-11-22 Reports/Paper1.Rmd
edit sig labels on sup fig 2

visit_cor=age_wide_methyl%>%
  ggplot(aes(x=`Age 9`, y=`Age 15`))+geom_point()+stat_cor()+geom_smooth(method=lm)+theme_classic()+
  scale_x_continuous('Age 9 score')+scale_y_continuous('Age 15 score')+
  facet_wrap(~Methyl_factor, scales='free', labeller = labeller(Methyl_factor=all_methyl_labels), ncol=3)

>>>>

visit_cor=age_wide_methyl%>%
  ggplot(aes(x=`Age 9`, y=`Age 15`))+geom_point(size=1)+stat_cor(label.sep=', ', size=2.5, label.y.npc=0.95)+geom_smooth(method=lm)+theme_classic()+
  scale_x_continuous('Age 9 score')+scale_y_continuous('Age 15 score')+
  facet_wrap(~Methyl_factor, scales='free', labeller = labeller(Methyl_factor=all_methyl_labels), ncol=3)
